My interest in secure and reliable systems developed during my Master’s studies in Information Security at Tampere University, where I focused on applied cryptography and secure software. This led me to my current role as a Researcher, contributing to the integration of post-quantum cryptography into platforms such as OpenSSL and Firefox. Working on security-critical components taught me to take ownership of complex problems, approach challenges methodically, and build solutions that are dependable and maintainable.

Equally important has been learning through collaboration. I regularly work with supervisors and peers to design solutions, review implementations, and resolve technical issues. This experience strengthened my ability to communicate clearly, adapt to feedback, and contribute effectively in team environments where shared responsibility and continuous improvement are essential.

I am applying to Nordea’s Graduate Programme in AI, Tech \& Data because I want to contribute to building secure and scalable technology that supports real-world financial systems. Nordea’s emphasis on combining technology, data, and security aligns closely with my background and interests. I am motivated to contribute with curiosity, responsibility, and a strong technical foundation while continuing to grow within Nordea’s collaborative and forward-looking environment. 

Please find my resume attached, which details my qualifications for the position. If you have any
questions, please do not hesitate to contact me and I look forward to discussing my qualifications with
you personally. Thank you for your time and consideration.
